A parallelised and distributed approach to implementing Conway's Game of Life

### 2022-12-02 report/article_2.tex
fixed misspelling, para 1

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

@@

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A parralelized and distributed approach to implementing Conway's Game of Life} % Article title
\author{%
\textsc{Aaron Chan}\thanks{A thank you or further information} \\[1ex] % Your name
\normalsize University of bristol \\ % Your institution
\normalsize {ho21739@bristol.ac.uk} % Your email address
\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
\textsc{Ferdinand Hubbard}\thanks{Corresponding author} \\[1ex] % Second author's name
\normalsize University of bristol \\ % Your institution
\normalsize {ej21378@bristol.ac.uk} % Your email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{
\begin{abstract}
  In this report, we will explain our two solutions for implementing Conway's Game of Life in golang. The first solution is designed to be run on a
  single machine, and makes use of all the cpu threads available on a computer through the parralelization of the program. The second solution is designed
  to run on multiple machines, allowing for the work to be distributed accross multiple machines. This second solution uses aspects of the first solution
  within each worker.
\end{abstract}
}

@@

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------
\section{Introduction to the parralelized solution}

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item single threaded implemementation
  \item events passing (alive cells, turn completed)
  \item PGM image output implementation
  \item SDL implemementation (flipped cells events)
  \item using channels and goroutines to create multiple workers (parralelizing the solution)
  \item switching to a memory sharing solution instead of using channels (TODO?)
  \item implementing halo exchange
\end{itemize}
%------------------------------------------------

@@

\section{parralelizing the program}

@@

\section{parralelizing benchmark and critical analysis}

@@

\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\blindtext % Dummy text

>>>>

\usepackage[hmarginratio=5:5,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

@@

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{A parallelised and distributed approach to implementing Conway's Game of Life} % Article title
\author{%
\textsc{Aaron Chan}\\[1ex] % Your name
\normalsize University of Bristol \\ % Your institution
\normalsize {ho21739@bristol.ac.uk} % Your email address
\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
\textsc{Ferdinand Hubbard}\\[1ex] % Second author's name
\normalsize University of Bristol \\ % Your institution
\normalsize {ej21378@bristol.ac.uk} % Your email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{
\begin{abstract}
  We intend to explain our two solutions for implementing Conway's Game of Life in Golang, namely the Parallel and Distributed versions.
  Within this report, we will discuss the impacts of thread usage in both our implementations, as well as the effect of distributed computation as opposed to single-machine computation. In essence, we found that execution time was sped up as we increased thread count, reduced branch instructions and implemented a halo exchange mechanism.
\end{abstract}
}

@@

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------
\section{Introduction to the parallelised solution}

As an initial attempt, we began by implementing a single-threaded Game of Life (GoL) Engine, expanding upon this work with parallelisation by virtue of concurrent go-routine workers. Recognising that branch instructions throttled efficiency of \texttt{getNeighbourCount}, we removed if-statements, introduced bit-masking and assignment which drastically improving runtime.

\begin{itemize}
  \item single threaded implementation
  \item events passing (alive cells, turn completed)
  \item PGM image output implementation
  \item SDL implementation (flipped cells events)
  \item using channels and goroutines to create multiple workers (parallelising the solution)
  \item switching to a memory sharing solution instead of using channels (TODO?)
  \item implementing halo exchange
\end{itemize}
%------------------------------------------------

@@

\section{parralelising the program}

@@

\section{parallelising benchmark and critical analysis}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit.
\blindtext % Dummy text
